Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-12-01 paper/structureScene.tex
typo: rather -> rather than

%The same division is found in the field of auditory scene analysis, wherein the interest may either be 1) to isolate and identify precise events, \ie acoustic event detection (AED), or 2) to predict global attributes assigned to large time spans of audio, \ie acoustic scene classification (ASC).
To do so, a popular approach for acoustic scene modeling is the bag-of-frames (BOF) approach introduced by Aucouturier et al. \cite{aucouturier2007bag}, where a scene is modeled by high-level summary statistics computed from local features.
Being a very generic method, this approach has been applied to many audio classification tasks besides ASC.
Yet the proposed implementation using Gaussian mixture models (GMMs) of mel-frequency cepstral coefficients (MFCCs) has been demonstrated to perform comparably to a mere averaging of the features \cite{lagrange:hal-01082501}.
Indeed, the typical morphology of acoustic scenes is of a ``skeleton of events on a bed of textures'' \cite{nelken2013}, with a few discrete sound events superimposed upon a stationary acoustic background.
Therefore, it is arguably more beneficial to focus on the large-scale temporal evolution of auditory scenes rather on the joint probability distribution of short-term features.

>>>>

%The same division is found in the field of auditory scene analysis, wherein the interest may either be 1) to isolate and identify precise events, \ie acoustic event detection (AED), or 2) to predict global attributes assigned to large time spans of audio, \ie acoustic scene classification (ASC).
To do so, a popular approach for acoustic scene modeling is the bag-of-frames (BOF) approach introduced by Aucouturier et al. \cite{aucouturier2007bag}, where a scene is modeled by high-level summary statistics computed from local features.
Being a very generic method, this approach has been applied to many audio classification tasks besides ASC.
Yet the proposed implementation using Gaussian mixture models (GMMs) of mel-frequency cepstral coefficients (MFCCs) has been demonstrated to perform comparably to a mere averaging of the features \cite{lagrange:hal-01082501}.
Indeed, the typical morphology of acoustic scenes is of a ``skeleton of events on a bed of textures'' \cite{nelken2013}, with a few discrete sound events superimposed upon a stationary acoustic background.
Therefore, it is arguably more beneficial to focus on the large-scale temporal evolution of auditory scenes rather than on the joint probability distribution of short-term features.
